03 - Analyses coding

### 2022-07-08 scripts/r/03_analyses_coding.Rmd
♻️ - add descriptive plots to 03_analyses_coding

coding <- read_sheet(the_sheet) %>%
  mutate(
    outcome = factor(outcome, levels = c("duration", "f0", "formants", "intensity", "harmonics", "SNR", "multivariate", "other")),
    temporal_window = factor(temporal_window, levels = c("segment", "syllable", "word", "phrase", "sentence", "other"))
  )

@@

@@

@@

@@

```{r}
coding %>%
  select(framework:operationalisation, temporal_window, typicality_operationalization, random_effects) %>%
  distinct()
```

>>>>

coding <- read_sheet(the_sheet) %>%
  mutate(
    outcome = factor(outcome, levels = c("duration", "f0", "formants", "intensity", "harmonics", "SNR", "multivariate", "other")),
    temporal_window = factor(temporal_window, levels = c("segment", "syllable", "word", "phrase", "sentence", "other"))
  ) %>%
  drop_na(model_id)

@@

```{r}
coding %>%
  ggplot(aes(framework)) +
  geom_bar()
```

@@

```{r}
coding %>%
  ggplot(aes(family)) +
  geom_bar()

coding %>%
  ggplot(aes(outcome, fill = family)) +
  geom_bar()
```

@@

```{r}
coding %>%
  count(operationalisation) %>%
  ggplot(
    aes(reorder(operationalisation, desc(n)), n)
    ) +
  geom_bar(stat = "identity")
```

@@

```{r}
coding %>%
  select(framework:outcome, operationalisation, temporal_window, typicality_operationalization, random_effects) %>%
  distinct()
```
